---
title: "Google Analytics dashboard"
author: "statsandr.com"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: embed
    social: ["twitter", "facebook", "linkedin"]
---

```{r setup, include=FALSE}
library(flexdashboard)
library(readr)
library(ggplot2)
library(dplyr)
library(reactable)
library(lubridate)
library(stringr)
library(googleAnalyticsR)

# specify an email you have already authenticated with once outside of Rmd
ga_auth(email = "ant.soetewey@gmail.com")

accounts <- ga_account_list()
# accounts
accounts$webPropertyName

# select the view ID by property name
view_id <- accounts$viewId[which(accounts$webPropertyName == "statsandr.com")]

# set date range
start_date <- as.Date("2019-12-16")
end_date <- Sys.Date() - 1

# get Google Analytics (GA) data
gadata0 <- google_analytics(view_id,
  date_range = c(start_date, end_date),
  metrics = c("users", "pageviews"),
  anti_sample = TRUE # slows down the request but ensures data isn't sampled
)

gadata1 <- google_analytics(view_id,
  date_range = c(start_date, end_date),
  metrics = c("pageviews"),
  dimensions = c("date"),
  anti_sample = TRUE # slows down the request but ensures data isn't sampled
)

gadata2 <- google_analytics(view_id,
  date_range = c(start_date, end_date),
  metrics = c("pageviews"),
  dimensions = c("pageTitle"),
  anti_sample = TRUE # slows down the request but ensures data isn't sampled
)
gadata2 <- subset(gadata2, pageviews > 500)

theme_set(theme_minimal())

users_color <- "purple"
pageviews_color <- "forestgreen"
```

Row
-----------------------------------------------------------------------

### users {.value-box}

```{r}
valueBox(
  value = paste(format(sum(gadata0$users), big.mark = ","), "", sep = " "),
  caption = "Users",
  icon = "far fa-user",
  color = users_color
)
```

### pageviews {.value-box}

```{r}
valueBox(
  value = paste(format(sum(gadata0$pageviews), big.mark = ","), "", sep = " "),
  caption = "Page views",
  icon = "far fa-file-alt",
  color = pageviews_color
)
```

Row {.tabset}
-----------------------------------------------------------------------

### Page views

```{r}
gadata_by_day <- gadata1 %>% 
  group_by(date) %>% 
  summarize(pagesums = sum(pageviews))

# scatter plot with a trend line
gadata1 %>%
  ggplot(aes(x = date, y = pageviews)) +
  geom_point(size = 1L, color = "steelblue") + # change size and color of points
  geom_smooth(color = "darkgrey", alpha = 0.25) + # change color of smoothed line and transparency of confidence interval
  labs(
    y = "Page views",
    x = ""
    # title = "Daily evolution of page views,
    # subtitle = paste0(format(start_date, "%b %d, %Y"), " to ", format(end_date, "%b %d, %Y")),
    # caption = "Data: Google Analytics data of statsandr.com"
  ) +
  theme(plot.margin = unit(c(5.5, 15.5, 5.5, 5.5), "pt")) + # to avoid the plot being cut on the right edge
  scale_y_continuous(labels = scales::comma) # better y labels
```

### Most popular posts

```{r}
# gadata_most_popular <- gadata2 %>% 
#   count(pageTitle, wt = pageviews, sort=TRUE)

# reactable(gadata_most_popular,
#            columns = list(pageTitle     = colDef(name = "Title",
#                                             align = "left"),
#                           n             = colDef(name = "Page views")),
#             pagination = TRUE,
#             searchable = TRUE,
#             striped = TRUE)

most_viewed_posts <- gadata2 %>%
  mutate(Title = str_trunc(pageTitle, width = 40)) %>% # keep maximum 40 characters
  count(Title, wt = pageviews, sort = TRUE)

# plot
top_n(most_viewed_posts, n = 15, n) %>% # edit n for more or less pages to display
  ggplot(., aes(x = reorder(Title, n), y = n)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(
    y = "Page views",
    x = ""
    # title = "Top performing pages in terms of page views",
    # subtitle = paste0(format(start_date, "%b %d, %Y"), " to ", format(end_date, "%b %d, %Y")),
    # caption = "Data: Google Analytics data of statsandr.com"
  ) +
  scale_y_continuous(labels = scales::comma) # better y labels
```

### About

**Custom Google Analytics dashboard**

This [custom Google Analytics dashboard](https://statsandr.com/blog/files/google-analytics-dashboard/) provides an overview of the evolution of page views and the most popular posts for the blog [statsandr.com](https://statsandr.com/). This dashboard is built with R using the R Markdown framework.

**Code**

The code behind this dashboard is available on [GitHub](https://github.com/AntoineSoetewey/Google-Analytics-dashboard){target="_blank"}. Feel free to adapt the code to your needs.

**Data**

The input data for this dashboard is the Google Analytics data of [statsandr.com](https://statsandr.com/), for the period from `r paste0(format(start_date, "%b %d, %Y"), " to ", format(end_date, "%b %d, %Y"))`.

**Information & contact**

More information on how to track the performance of your blog or website can be found in this [article](https://statsandr.com/blog/track-blog-performance-in-r/).

For any question or feedback, you can either open an [issue](https://github.com/AntoineSoetewey/Google-Analytics-dashboard/issues){target="_blank"} or [contact me](https://statsandr.com/contact/).


*Go back to [statsandr.com](https://statsandr.com/) (blog) or [antoinesoetewey.com](https://www.antoinesoetewey.com/) (personal website).*
